Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex
updated paper

	 We detail the methods in the following sections.  
 	\subsection{Part-of-Speech}
 	\subsection{Semantic Knowledge base}
        \indent We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.

@@

        We also used semantic similarity methods on the brown corpus, using an implementation by the same author as Lesk's algorithm. [CITATION] We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates. However, each method was only accurate for certain words, but none of them could consistently identify the correct word sense.
	\subsection{Supervised LSA}
	Our approach uses simple LSA with a supervised learning component.

@@

>>>>

	 We detail the methods in the following sections.  
 	\subsection{Part-of-Speech}
 	We constructed two POS bigram models to try and perform coarse-filtering on the data by identifying the senses we could predict with high probability using a part-of-speech model before propogating the data instances further down the pipeline. We constructed one bigram model consisting of the POS bigrams containing the word coming before the target word and the target word, and another bigram model consisting of the POS bigrams containing the target word and word following the target word. The POS tags were generated by running NLTK's POS-tagger on the sentence containing the target word in each of our training data instances. On an input test instance, we would tag the sentence of interest, extract the two bigrams containing the target word, check if either bigram could be found in either of our bigram models, and output a predicted sense key if our predicted probability of the sense key given that bigram exceeded 80\%. To avoid skewed probabilities from having only one training data instance with that bigram, but also to ensure sufficient coverage for the already sparse data set, we also set a frequency count threshold of three such that we would only output our predicted sense key if we had seen more than three instances of this particular bigram in our training data and we predicted a probability of over 80\%.
 	\subsection{Semantic Knowledge base}
        \indent We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.

@@

        We also used semantic similarity methods on the brown corpus, using an implementation by the same author as Lesk's algorithm. [CITATION] We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates. However, each method was only accurate for certain words, but none of them could consistently identify the correct word sense.

        We also tried Naive Bayes approach using two bigram models similar to the method used for our part of speech models, with one bigram model for bigrams including the word before the target word and the target word, and another bigram model for the target word and the word after the target word. This too had a low accuracy rate so we did not include it in our pipeline.
	\subsection{Supervised LSA}
	Our approach uses simple LSA with a supervised learning component.

@@

    9. ACL-SIGLEX. 2001. Evaluation Exercises for the Semantic Analysis of Text. Retrieved from http://www.senseval.org/.
